Token-level author diarization using clustering of stylistic contexts

### 2017-06-01 paper/paper.tex
Tables 2 and 3 updated.

\begin{table*}
	\caption{Results on the intrinsic plagiarism detection task.}
	\label{tab:narrow-table}
	\begin{center}
		\begin{tabular}{l|ccc|ccc}
			\toprule
			Method & $R_\mathrm{\mu}$ & $P_\mathrm{\mu}$ & $F_\mathrm{\mu}$ & $R_\mathrm{M}$ & $P_\mathrm{M}$ & $F_\mathrm{M}$\\
			\midrule
			Single-author dummy BL 	& 0.13 & 1.00 & 0.22 & 0.13 & 1.00 & 0.22 \\
			Stochastic dummy BL 	& 0.13 & 0.94 & 0.23 & 0.15 & 0.94 & 0.25 \\
			Simple dummy BL 		& 0.13 & 0.24 & 0.14 & 0.13 & 0.24 & 0.13 \\
			\midrule
			\citet{kuznetsov-2016} 	& 0.19 & 0.29 & 0.22 & 0.15 & 0.28 & 0.17 \\
			\citet{sittar-2016} 	& 0.07 & 0.14 & 0.08 & 0.10 & 0.14 & 0.10 \\
			\midrule			
			Model A 				&  &  &  &  &  & \\			
			Model B (linear) 		& 0.21 & 0.35 & 0.23 & 0.21 & 0.34 & 0.22 \\
			Model B (weighting) 	& 0.24 & 0.36 & 0.23 & 0.24 & 0.34 & 0.23 \\
			\bottomrule
		\end{tabular}
	\end{center}
\end{table*}

@@

\begin{table*}
	\caption{Results on the author diarization task with known number of authors.}
	\label{tab:narrow-table}
	\begin{center}
		\begin{tabular}{l|ccc|ccc}
			\toprule
			\multirow{2}{*}{Method} & \multicolumn{3}{c|}{Task \emph{b}} & \multicolumn{3}{c}{Task \emph{c}} \\
			\cmidrule{2-7}
			& $R_{\mathrm{B}^3}$ & $P_{\mathrm{B}^3}$ & $F_\mathrm{\mathrm{B}^3}$ & $R_{\mathrm{B}^3}$ & $P_{\mathrm{B}^3}$ & $F_\mathrm{\mathrm{B}^3}$ \\
			\midrule
			Single-author dummy BL 		& 0.33 & 1.00 & 0.47 & 0.37 & 1.00 & 0.52 \\
			Stochastic dummy BL 		& 0.35 & 0.59 & 0.41 & 0.39 & 0.59 & 0.45 \\
			Simple dummy BL 			& 0.43 & 0.50 & 0.45 & 0.45 & 0.54 & 0.45 \\
			\midrule
			\citet{kuznetsov-2016}		& 0.46 & 0.64 & 0.52 & 0.42 & 0.64 & 0.48 \\
			\citet{sittar-2016} 		& 0.47 & 0.28 & 0.32 & 0.47 & 0.31 & 0.35 \\
			\midrule			
			Model A 					&  &  &  &  &  & \\			
			Model B (linear) 			& 0.48 & 0.45 & 0.46 & 0.56 & 0.82 & 0.64 \\
			Model B (weighting)			& 0.51 & 0.49 & 0.50 & 0.57 & 0.77 & 0.64 \\
			\bottomrule
		\end{tabular}
	\end{center}
\end{table*}

>>>>

\begin{table*}
	\caption{Results on the intrinsic plagiarism detection task.}
	\label{tab:narrow-table}
	\begin{center}
		\begin{tabular}{l|ccc|ccc}
			\toprule
			Method & $P_\mathrm{\mu}$ & $R_\mathrm{\mu}$ & $F_\mathrm{\mu}$ & $P_\mathrm{M}$ & $R_\mathrm{M}$ & $F_\mathrm{M}$\\
			\midrule
			Single-author dummy BL 	& 0.13 & 1.00 & 0.22 & 0.13 & 1.00 & 0.22 \\
			Stochastic dummy BL 	& 0.13 & 0.94 & 0.23 & 0.15 & 0.94 & 0.25 \\
			Simple BL 				& 0.13 & 0.24 & 0.14 & 0.13 & 0.24 & 0.13 \\
			\midrule
			\citet{kuznetsov-2016} 	& 0.29 & 0.19 & 0.22 & 0.28 & 0.15 & 0.17 \\
			\citet{sittar-2016} 	& 0.14 & 0.07 & 0.08 & 0.14 & 0.10 & 0.10 \\
			\midrule			
			Model A 				&  &  &  &  &  & \\			
			Model B (linear) 		& 0.21 & 0.35 & 0.23 & 0.21 & 0.34 & 0.22 \\
			Model B (weighting) 	& 0.24 & 0.36 & 0.23 & 0.24 & 0.34 & 0.23 \\
			\bottomrule
		\end{tabular}
	\end{center}
\end{table*}

@@

\begin{table*}
	\caption{Results on the author diarization task.}
	\label{tab:narrow-table}
	\begin{center}
		\begin{tabular}{l|ccc|ccc}
			\toprule
			\multirow{2}{*}{Method} & \multicolumn{3}{c|}{Task \emph{b}} & \multicolumn{3}{c}{Task \emph{c}} \\
			\cmidrule{2-7}
			& $P_{\mathrm{B}^3}$ & $R_{\mathrm{B}^3}$ & $F_\mathrm{\mathrm{B}^3}$ & $P_{\mathrm{B}^3}$ & $R_{\mathrm{B}^3}$ & $F_\mathrm{\mathrm{B}^3}$ \\
			\midrule
			Single-author dummy BL 		& 0.33 & 1.00 & 0.47 & 0.37 & 1.00 & 0.52 \\
			Stochastic dummy BL 		& 0.35 & 0.59 & 0.41 & 0.39 & 0.59 & 0.45 \\
			Simple BL 					& 0.43 & 0.50 & 0.45 & 0.45 & 0.54 & 0.45 \\
			\midrule
			\citet{kuznetsov-2016}		& 0.64 & 0.46 & 0.52 & 0.64 & 0.42 & 0.48 \\
			\citet{sittar-2016} 		& 0.28 & 0.47 & 0.32 & 0.31 & 0.47 & 0.35 \\
			\midrule			
			Model A 					&  &  &  &  &  & \\			
			Model B (linear) 			& 0.48 & 0.45 & 0.46 & 0.56 & 0.82 & 0.64 \\
			Model B (weighting)			& 0.51 & 0.49 & 0.50 & 0.57 & 0.77 & 0.64 \\
			\bottomrule
		\end{tabular}
	\end{center}
\end{table*}
